Hydras \& Co.

### 2023-12-04 doc/chapter-primrec.tex
Small correction (doc)

\begin{todo}
Fix the display the local definition of \texttt{x} in the following proof.
\end{todo}

>>>>

\begin{remark}
In the following snippet,  \emph{Alectryon}'s \texttt{Latex} generator  prints the \emph{local definition} of $x$ (as the maximum of $2$ and $m$) as a simple \emph{declaration} \texttt{x: nat}.
Thus the proof script is correct, but the three last sub-goals are not correctly displayed, since 
they do not show how the inequalities $2\leq x$ and $m \leq x$ could be inferred by \texttt{lia}.
\end{remark}
